The black-hole ringdown as a probe of higher-curvature gravity theories

### 2021-12-21 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: removed duplicate bib entry; added package for slanted signs
hs: filling more details of table/re-organizing subsections

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-2}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
% \usepackage{times}
% \usepackage[varg]{txfonts}
\usepackage{txfonts}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{mathrsfs}
%\linenumbers
\usepackage{makecell}
\usepackage{microtype}

\definecolor{LinkColor}{rgb}{0.75, 0, 0}
\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
\definecolor{UrlColor}{rgb}{0, 0, 0.75}
\hypersetup{linkcolor=LinkColor}
\hypersetup{citecolor=CiteColor}
\hypersetup{urlcolor=UrlColor}
\usepackage{perpage}
\MakePerPage{footnote}

@@

% HS: temporary title. Feel free to add suggestions
% \title{Probing higher-curvature gravity theories from binary black hole ringdown signals}
\title{Black-hole ringdown as probe of higher-curvature gravity theories}

\author{Abhirup Ghosh}
\author{Hector O. Silva}
\AEI
\author{Alessandra Buonanno}
\AEI
\UMD

@@

\maketitle
\tableofcontents

@@

@@

\hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}

@@

\hs{Here we present a short review of~\cite{Brito:2018rfr,Ghosh:2021mrv} and
explain how we modified it to include the {\sc Parspec} parametrisation.}

@@

\hs{Here we review class of gravity theories we will consider.
They all have higher-curvature terms, hence the `higher-curvature gravity theories'
in the title.}

A broad class modified gravity theories are described by the action
%
\begin{equation}
S = \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
\left[ R
- \tfrac{1}{2}(\nabla \varphi)^2
\right]
+
\sum_{n \geqslant 2} \frac{\ell^{2n - 2}}{16 \pi G} S^{(2n)},
\end{equation}
%
where $\varphi$ is a dynamical scalar field, $\ell$ some length scale, assumed
to be small compares to the length scale associated with a black hole, i.e.,
$GM \gg \ell$, and $S^{(2n)}$ are corrections to the Einstein-Klein-Gordon
action that introduce involving higher-order curvature tensors (with $2n$
metric derivatives) and scalar field.

@@

%%%%%%%%%%%%%%%%%
\section{Methods}
\label{sec:methods}
%%%%%%%%%%%%%%%%%

@@

\begin{table*}[th]
\begin{tabular}{c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega$ & $\delta \tau$ & QNM & Constraint \\
\hline
sGB      & 4 & \dots & \dots & \cite{Pierini:2021jxd} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 1.7$~km~\cite{Perkins:2021mhb} \\
dCS      & 4 & \dots & \dots & \cite{Wagle:2021tam} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 8.5$~km~\cite{Silva:2020acr} \\
cEFTofGR & 4 & \dots & \dots & \cite{Cano:2021myl} & -- \\
qEFTofGR & 6 & \dots & \dots & \cite{Cano:2021myl} & -- \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega$ and decay time $\delta \tau$, the
references from which we used the results from and the current best constraint
(if applicable).
%
\hs{Add a column with the constraint (if any) that we placed.}
\hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

\subsection{Gravitational events used}

@@

\subsection{Parameter estimation}

%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}
%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele~Berti, Andrea~Maselli, Deyan~Mihailov and Serguei~Ossokine
for discussions.
%
We thank the computational resources provided by the AEI, specifically the
{\sc Hypatia} cluster.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%

>>>>

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-2}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{bm}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
\usepackage{txfonts}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{mathrsfs}
\usepackage{makecell}
\usepackage{microtype}

\definecolor{LinkColor}{rgb}{0.75, 0, 0}
\definecolor{CiteColor}{rgb}{0, 0.5, 0.5}
\definecolor{UrlColor}{rgb}{0, 0, 0.75}
\hypersetup{linkcolor=NavyBlue}
\hypersetup{citecolor=NavyBlue}
\hypersetup{urlcolor=NavyBlue}
\usepackage{perpage}
\MakePerPage{footnote}

@@

% HS: temporary title. Feel free to add suggestions
% \title{Probing higher-curvature gravity theories from binary black hole ringdown signals}
\title{The black-hole ringdown as a probe of higher-curvature gravity theories}

\author{Hector O. Silva}
\author{Abhirup Ghosh}
\AEI
\author{Alessandra Buonanno}
\AEI
\UMD

@@

\maketitle
% \tableofcontents

@@

\hs{AB will do this.}

@@

\hs{HS will do this.}
\hs{Here we briefly review~\cite{Maselli:2019mjd,Carullo:2021dui}.}

@@

\hs{AG will do this.}
\hs{Here we present a short review of~\cite{Brito:2018rfr,Ghosh:2021mrv} and
explain how we modified it to include the {\sc Parspec} parametrisation.}

@@

\hs{HS will do this.}

% \hs{Here we review class of gravity theories we will consider.
% They all have higher-curvature terms, hence the `higher-curvature gravity theories'
% in the title.}

A broad class modified gravity theories are described by the action
%
\begin{equation}
S = \frac{1}{16 \pi G} \int \dd^4x \sqrt{-g}
\left[ R
- \tfrac{\beta}{2}(\nabla \varphi)^2
\right]
+
\sum_{n \geqslant 2} \frac{\ell^{2n - 2}}{16 \pi G} S^{(2n)},
\end{equation}
%
where $\varphi$ is a dynamical scalar field, $\ell$ some length scale, assumed
to be small compares to the length scale associated with a black hole, i.e.,
$GM \gg \ell$, and $S^{(2n)}$ are corrections to the Einstein-Klein-Gordon
action that introduce involving higher-order curvature tensors (with $2n$
metric derivatives) and scalar field.

@@

@@

\hs{HS will do this.}

\begin{table*}[th]
\begin{tabular}{c | c c c c c c c c}
\hline
\hline
Theory & $p$ & $\delta \omega^{(0)}_{220}$ & $\delta \tau^{(0)}_{220}$ & $\delta \omega^{(1)}_{220}$ & $\delta \tau^{(1)}_{220}$ & QNM & Constraint & This work \\
\hline
sGB      & 4 & 0.0107 & 0.0044 & \dots & \dots & \cite{Pierini:2021jxd} & $\alpha^{1/2}_{\rm GB} \ell \leqslant 1.7$~km~\cite{Perkins:2021mhb} & \dots \\
dCS      & 4 & 3.1964 & 6.3619 & \dots & \dots &  \cite{Wagle:2021tam} & $\alpha^{1/2}_{\rm CS} \ell \leqslant 8.5$~km~\cite{Silva:2020acr} & \dots \\
cEFTofGR & 4 & $-0.3680$ / $-0.5131$  & 1.9242 / 1.7000 & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
qEFTofGR & 6 & \dots & \dots & \dots & \dots & \cite{Cano:2021myl} & --  & \dots \\
\hline
\hline
\end{tabular}
\caption{Summary of the quasinormal modes calculations.
%
We summarize each theory we have considered together with: the exponent $p$ at
which their QNM-modification enters, the corresponding modifications to the
oscillation frequency $\delta \omega^{(i)}_{220}$ and decay time $\delta \tau^{(i)}_{220}$, the
references from which we used the results from and the current best constraint
(if applicable).
%
In the entries for cEFTofGR, the first entries in the $\delta
\omega^{(i)}_{220}$, $\delta \tau^{(i)}_{220}$ are obtained by considering
\emph{only parity-even correnctions} and the second entries by considering
\emph{only parity-odd corrections}. In these cases, the dimensionless parameters
$\lambda_{\rm e,o}$ are degenerate with the lengthscale $\ell$.
%
\hs{Add a column with the constraint (if any) that we placed.}
\hs{TODO: add which runs are done and which need to be done.}
}
\label{tab:ref_theories_qnms}
\end{table*}

@@

%%%%%%%%%%%%%%%%%
\section{Analysis using LIGO-Virgo data}
\label{sec:results}
%%%%%%%%%%%%%%%%%

@@

@@

%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}
\label{sec:acknowledgements}
%
We thank Emanuele~Berti, Andrea~Maselli, Caio~F.~B.~Macedo, Deyan~Mihailov, and
Serguei~Ossokine for discussions.
%
We thank the computational resources provided by the AEI, specifically the
{\sc Hypatia} cluster.
%
The authors would like to thank everyone at the frontline of the Covid-19
pandemic.
%%%%%%%%%%%%%%%%%
